Evaluating photometric redshift PDF approaches for \textsc{LSST}

### 2019-03-08 paper/main.tex
clarification in abstract

Many scientific investigations of photometric galaxy surveys require redshift estimates, whose uncertainty properties are best encapsulated by photometric redshift (photo-$z$) posterior probability distribution functions (PDFs).
A plethora of photo-$z$ PDF estimation methodologies abound, producing discrepant results with no consensus on a preferred approach.
We present the results of a comprehensive experiment comparing twelve photo-$z$ algorithms on mock data produced for the Large Synoptic Survey Telescope (\textsc{LSST}) Dark Energy Science Collaboration (\textsc{DESC}).
By supplying perfect prior information, in the form of the complete template library and a representative training set as inputs to each code, we demonstrate the impact of the assumptions underlying each technique on the output photo-$z$ PDFs.
In the absence of a notion of true, unbiased photo-$z$ PDFs, we evaluate and interpret multiple metrics of the ensemble properties of the derived photo-$z$ PDFs as well as traditional reductions to photo-$z$ point estimates.
We report systematic biases and overall over/under-breadth of the photo-$z$ PDFs of many popular codes, which may indicate avenues for improvement in the algorithms or implementations.
Furthermore, we raise attention to the limitations of established metrics for assessing photo-$z$ PDF accuracy and identify the conditional density estimate (CDE) loss as a promising metric of photo-$z$ PDF performance in the case where true redshifts are available but true photo-$z$ PDFs are not.

>>>>

Many scientific investigations of photometric galaxy surveys require redshift estimates, whose uncertainty properties are best encapsulated by photometric redshift (photo-$z$) posterior probability distribution functions (PDFs).
A plethora of photo-$z$ PDF estimation methodologies abound, producing discrepant results with no consensus on a preferred approach.
We present the results of a comprehensive experiment comparing twelve photo-$z$ algorithms on mock data produced for the Large Synoptic Survey Telescope (\textsc{LSST}) Dark Energy Science Collaboration (\textsc{DESC}).
By supplying perfect prior information, in the form of the complete template library and a representative training set as inputs to each code, we demonstrate the impact of the assumptions underlying each technique on the output photo-$z$ PDFs.
In the absence of a notion of true, unbiased photo-$z$ PDFs, we evaluate and interpret multiple metrics of the ensemble properties of the derived photo-$z$ PDFs as well as traditional reductions to photo-$z$ point estimates.
We report systematic biases and overall over/under-breadth of the photo-$z$ PDFs of many popular codes, which may indicate avenues for improvement in the algorithms or implementations.
Furthermore, we raise attention to the limitations of established metrics for assessing photo-$z$ PDF accuracy; though we identify the conditional density estimate (CDE) loss as a promising metric of photo-$z$ PDF performance in the case where true redshifts are available but true photo-$z$ PDFs are not, we emphasize the need for science-specific performance metrics.
